---
title: My dynamic report
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```
```{css}
body {
  font-family: 'Helvetica Neue', Arial, sans-serif;
  max-width: 800px;
  margin: auto;
  padding: 20px;
  line-height: 1.6;
  color: #333;
}

h2 {
  color: #1a1a2e;
  border-bottom: 2px solid #e94560;
  padding-bottom: 5px;
}

h3 {
  color: #16213e;
}
```

## Tracking my YouTube watching habits

Over a two-week period in March 2026, I logged every YouTube video I watched using a Google Form. Each entry captured the video category, length in minutes, how I found the video, and a personal rating out of 10. The goal was to uncover patterns in what I watch, how I find content, and whether I actually enjoy what the algorithm serves me.
```{r data}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQxfs-eL_mktuY6n9cE8dVwBeFmOwY_9Czls7EUIf9oL-1FDI24W1tSkhn9ZG575Tgg55gbCS4s1Koq/pub?gid=2080505976&single=true&output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    category = `What category best describes this video?`,
    length_mins = `How long was the video in minutes?`,
    discovery = `How did you find this video?`,
    rating = `Rate this video from 1 to 10`
  )
```
```{r summary_values}
mean_length <- round(mean(latest_data$length_mins), 1)
mean_rating <- round(mean(latest_data$rating), 1)
prop_recommended <- round(sum(latest_data$discovery == "YouTube homepage/recommendation") / nrow(latest_data) * 100, 1)
total_videos <- nrow(latest_data)
```

### At a glance

Over the logging period, I watched a total of **`r total_videos`** videos. The average video length was **`r mean_length` minutes**, and my average rating was **`r mean_rating` out of 10**. Notably, **`r prop_recommended`%** of videos I watched came from YouTube's homepage or recommendation algorithm.

### What am I watching?
```{r bar_chart_1}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = reorder(category, category, function(x) -length(x)),
               fill = category)) +
  labs(
    title = "What do I watch on YouTube?",
    subtitle = "Number of videos watched by category over two weeks",
    x = "Video category",
    y = "Number of videos",
    caption = "Source: Personal YouTube watching log, March 2026"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

Music videos made up the largest share of my viewing, followed by Entertainment/Comedy and News/Politics. Education and Self Help content appeared less frequently, while Technology had only a single entry.

### How am I finding these videos?
```{r bar_chart_2}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = category, fill = discovery)) +
  labs(
    title = "How do I find the videos I watch?",
    subtitle = "Discovery method across video categories over two weeks",
    x = "Video category",
    y = "Number of videos",
    fill = "Discovery method",
    caption = "Source: Personal YouTube watching log, March 2026"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```

The YouTube homepage and recommendation algorithm dominated how I found content, accounting for `r prop_recommended`% of all videos. Searching and shared links were more common for News/Politics and Self Help content, suggesting I actively seek out those categories rather than passively consuming them.
